Observations

### 2020-05-08 exp_eth_val.Rmd
Add files via upload

# First Section (Tab: \ref{tab:First})

* Aim:
    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation; how $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
* Focus: relative group size for ethnicity and value distribution within each ethnic group, considering how they directly influence probability to sort with similars; interaction with levels of $\beta_e$,$\beta_v$
* Assumption: 
    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape) depending on level of global $\beta_e$ and $\beta_v$
    + equal ethnic size (blue/orange: $0.50$) vs majority/minority (blue/orange: $0.80$)
    + value distribution within each ethnic group: proportion circle/square, moving from minority circle to majority cirlce:  $0.20$,$0.50$,$0.80$. It can be seen as moving from more intolerant to  more intolerant society when value-dependent heterogeneous preferences are included. In this section, there is not heterogeneous preferences
* Figures:
    + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model. I identified $\beta =5$ for both ethnic and value preferences as threshold between area of high randomness and low randomness. Results can be explained as within the space resulting from area of high randomness and low randomness (i.e. high systematic component) for ethnic and value utility.
    + Relative group sizes: the bold frame in Fig: \ref{fig:global} would represent the baseline, where each subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the population and has probability $0.25$ to meet an agent of same ethnicity and same value (baseline: blue/orange = $0.5$ and within each ethnic group cirlce/square = $0.5$)
    + Relative group sizes (value orientation): in each figure from Fig: \ref{fig:global} to Fig: \ref{fig:crlblmajority} along the diagonal, moves from minority circle (low corner) in the population to majority circle (upper corner)
    + x-axis = ethnic weight $\beta_e$, y-axis = value weight $\beta_v$

@@

# Second Section (heterogeneous preferences for tolerant and intolerants)

* Aim:
    + Test the effect of heterogeneous preferences for two value groups, i.e. circle value-oriented care more about value than ethnic neighborhood composition, square ethnicity-oriented care more about ethnic than value composition
    + This would relate to the difference between tolerant (circle) and intolerant (square) as in the ACS paper and that we discussed
    + Observe how heterogeneity in agents' preferences along two value oriented groups will affect results in the previous section, through their mutual adaptation
    + Interaction between heterogeneous preferences and relative group sizes for both dimensions (here only equal ethnic and value group)
* Assumption: 
    + Agents hold both ethnic and value preferences, but $\beta$ for each dimension depends on their value orientation, either circle or square. Not difference due to ethnic membership are taken into consideration
    + Given the linear function, utility increases with value or ethnic homogeneity of neighborhood, but determinism component $\beta_e$ and $\beta_v$ are differently distributed to value groups: ethnic preferences of circle cannot be higher than value preferences ($\beta^{\circ}_e \leq \beta^{\circ}_v$) and value preferences of square cannot be higher than thier value preferences ($\beta^{\square}_v \leq \beta^{\square}_e$)
    + Ideally also condition of ethnic majority/minority and circle majority/minority should be included. Here for matter of time it is reduced to equal ethnic group size (blue/orange $0.50$) and for each ethnic group equal value group (circle/square $0.50$). So, each of the four subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the global agents' population
* Figures:
    + I compare the ethnic and value segregation of both circle and square agents
    + Focus on the difference between ethnic and value segregation (being close to agents sharing both ethnicity and value)
    + To reduce observations given the numbers of parameters, I jump on 3 critical points individualized in the previous section: $\beta = 0$: total randomness, $\beta = 5$: min. determinism, $\beta = 10$: max determinism
    + For each value group, in the baseline I put on x-axis the difference between the highest reference $\beta$ of that group and the other one, i.e. $\beta_e - \beta_v$ for square, $\beta_v - \beta_e$ for circle. Considering the critical point, I repeat observation for reference $\beta = 5$: min. determinism, and $\beta = 10$: max determinism, $\beta = 0$ is included in bot. Thus, along the x-axis the group becomes more sensitive to the reference dimension, ethnicity for square group, value for circle group. I compare how the baseline condition changes for interaction of value and ethnic preferences of the other group faceting the 3 critical points $\beta = 0; \beta = 5;\beta = 10$

@@

## Comparison different value orientation
* Fig: \ref{fig:betatwoethnic}: x-axis $\beta^{\square}_e - \beta^{\square}_v$, on the top panel with $\beta^{\square}_e = 5$ (area of high randomness), on bottom panel  $\beta^{\square}_e = 10$ (area of low randomness). X-axis = 0,  ethnic and value utility have equal weight, along the x-axis ethnic weight prevails over value weight. the lower the distance between ethnic and value segregation, the more agents live close to others similar for both ethnicity and value.
* Viewing at lower left panel, where behavior of circle is totally random, not only the distance between ethnic and value segregation of square is lower when $\beta^{\square}_e = \beta^{\square}_v$ (x-axis 0), but also higher for both dimensions, progressing towards x-axis (ethnic becomes higher than 10), value segregation decreases, with more linear slope for high determinism area (bottom panel).
* It persists that each $\beta$ rules the reference dimension, but the random behavior of the other group decreases the segregation expected for that level of $\beta$, higher determinism of the other group increases  the level of segregation for that dimension. Demonstration, moving from $\beta^{\circ}_v = 5$ to  $\beta^{\circ}_v = 10$ 
* As $\beta^{\square}_e$ becomes higher than  $\beta^{\square}_v$, moving on the x-axis, ethnic segregation persists constantly, while value segregation diminishes.
* The threshold of $\beta = 5$ seen in the previous section is somehow replicated: in the top panel, max value and ethnic segregation are equal 1 when both  $\beta^{\square}_e = \beta^{\square}_v = 0$, on the x-axis 0, and value segregation declines once $\beta^{\square}_v$ comes close to 0. Looking at panel below (high determinism), the decline of value segregation occurs equally when $\beta^{\square}_v$ declines from 5 to 0 (on the right of red line 10-5:5 and so on)
* Even though the direct effect of $\beta_v$ is assumed and same patterns are observed from low determinism (top panel) and high determinism (bottom panel), the high determinism of  $\beta^{\square}_e$ is associated with very slight increase in the value segregation of square, also for same level of $\beta^{\square}_v = 0$, though negligeable
* The distance between ethnic and value segregation is higher in the middle panel, where circle hold same min utility preferences $\beta^{\circ}_e = \beta^{\circ}_v = 5$, and also square increase in ethnic over value preference (x-axis = 5). Basically the only random component is the value orientation of square agents, which has the same effect on both circle and square population patterns
* Moving on the diagonal, where $\beta^{\circ}_e = \beta^{\circ}_v = 10$, the distance between ethnic and value decreases, meaning agents are more likely to live close to agents of both same ethnicity and value: the increase in utility at max level of circle ($\beta^{\circ}_e = \beta^{\circ}_v = 10$) compensates for random value behavior of square, since circle will avoid neighborhoods with square 
* Fig: \ref{fig:betatwovalue} shows the similar trends, focusing on value segregation over ethnic segregation for the circle population. Nevertheless, in the middle panel ($\beta^{\square}_e = \beta^{\square}_v = 5$), I would expect symmetric scenario than in Fig: \ref{fig:betatwoethnic}, with ethnic segregation of circle being same as value segregatiion than square. Why here circle are completed ethnically integrared? There is a difference between the two dimensions? Think about.

```{r betatwoethnic,fig.pos='H',fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }

@@

ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

@@

```{r betatwovalue,  fig.pos="H",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }

@@

iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

>>>>

# First Section, relative group size & homogeneous preferences (Tab: \ref{tab:First})

* Aim:
    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation; how $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
* Focus: relative group size for ethnicity and value distribution within each ethnic group, considering how they directly influence probability to sort with similars; interaction with levels of $\beta_e$,$\beta_v$
* Assumptions: 
    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape) depending on level of global $\beta_e$ and $\beta_v$
    + equal ethnic size (blue/orange: $0.50$) vs majority/minority (blue/orange: $0.80$)
    + value distribution within each ethnic group: proportion circle/square, moving from minority circle to majority cirlce:  $0.20$,$0.50$,$0.80$. It can be seen as moving from more intolerant to  more intolerant society when value-dependent heterogeneous preferences are included. In this section, there is not heterogeneous preferences
* Figures:
    + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model. I identified $\beta =5$ for both ethnic and value preferences as threshold between area of high randomness and low randomness. Results can be explained as within the space resulting from area of high randomness and low randomness (i.e. high systematic component) for ethnic and value utility.
    + Relative group sizes: the bold frame in Fig: \ref{fig:global} would represent the baseline, where each subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the population and has probability $0.25$ to meet an agent of same ethnicity and same value (baseline: blue/orange = $0.5$ and within each ethnic group cirlce/square = $0.5$)
    + Relative group sizes (value orientation): in each figure from Fig: \ref{fig:global} to Fig: \ref{fig:crlblmajority} along the diagonal, moves from minority circle (low corner) in the population to majority circle (upper corner)
    + x-axis = ethnic weight $\beta_e$, y-axis = value weight $\beta_v$

@@

# Second Section, heterogeneous (hierarchical?) preferences value vs ethnicity (Tab: \ref{tab:Second})

* Aim:
    + Test the effect of heterogeneous preferences depending on value attribution: circle care more about value neighborhood composition, square care more about ethnic neighborhood composition.
    + This is the case  we discussed, adapting to circle tolerant, square intolerant
    + How preference heterogeneity affects results in  the previous section, where agents hold  same preference
    + How mutual adaptation of circle and square driven by different hierarchy of preference affect each other segregation patterns
    + Interaction of heterogeneous preferences with relative group size for ethnic and value membership
* Assumptions: 
    + square hold higher ethnic than value preferences: $\beta^{\square}_e \geq \beta^{\square}_v$; circle hold higher value than ethnic preferences: $\beta^{\circ}_v \geq \beta^{\circ}_e$.
    + No difference due to ethnic membership
    + \textbf{NOTE: Here only baseline} for question of time/computation server (Tab: \ref{tab:Second}). I'd collect conditions of majority and minority circle or square in ethnic different group sizes.
* Figures
    + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
    + Considering the critical levels of $\beta = 5$ between high randomness and low randomness (space model Fig: \ref{fig:baselineone}), I jump here directly to critical points $\beta = 0$: total ranomness,  $\beta = 5$: min determinism, $\beta = 10$: max determinism, this for each dimensions and faceting for circle and value group.
    + ANNEX B heatmaps: ethnic and value segregation for all preferences of square faceted for the 3 critical points of circle (Fig: \ref{fig:heatmapdsquare}); ethinic and value segregation for all preferences of circle faceted for the 3 critical points of square (Fig: \ref{fig:heatmapdcircle})
    + Fig: \ref{fig:betatwoethnic} and Fig: \ref{fig:betatwovalue} compares in the same graph ethnic and value segregation for circle and square agents, narrowing down compared to ANNEX B. Focus: the lower the distance between ethnic and value segregation, the more the agent relocates close to a members of the own ethnic and value subgroup (Fig: \ref{fig:thheory})

@@

## Focus on square preferences (Fig: \ref{fig:betatwoethnic})
* x-axis: difference preferences for square $\beta^{\square}_e - \beta^{\square}_e$. x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\square}_e = \beta^{\square}_v = 5$ top panel, $\beta^{\square}_e = \beta^{\square}_v = 10$ lower panel); proceding on x-axis, ethnic matters more to square than value ($\beta^{\square}_e$ is constant, while $\beta^{\square}_v$ decreases to 0)
* y-axis: ethnic and value segregation for circle and square
* bottom left box, where all circle relocate randomly ($\beta$ circle = 0):
   + bottom panel (high determinism): decline of value segregation for both groups occurs mostly linear monotonic for all values of $\beta^{\square}_v$
   + ethnic segregation of square population is lower than in other conditions, due to random relocation of circle, both for high ethnic and lower ethnic determinism (top and bottom figure)
* along the diagonal, as circle population increases equally ethnic and value determinism: 
   + value segregation for both groups decreases along x-axis, where value matters progressively less for square, given the constant level of square ethnic preference
   + decline of value segregation above happens in high value randomness when $\beta^{\square}_v \leq 5$: top panel: all conditions; bottom panel: right side of red line (10-5 = 5)
   + curve of value segregation decline is steeper in all conditions of the bottom panel (higher determinism $\beta^{\square}_e = 10$)
* above diagonal, ethnic and value segregation of square population decline the most for high values of $\beta^{\square}_e$ when circle relocate randomly for ethnicity. I relate this to high randomness of $\beta^{\square}_v < 5$: all conditions top panel, but only right side of red line, where $\beta^{\square}_v < 5$. The trend is higher in the top panel of high randomness. Basically seems high value and ethnic determinism of square support each other on relative segregation when the other circle group  relocates randomly.

```{r betatwoethnic,fig.pos='H',fig.out="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }

@@

ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

@@

## Focus on circle preferences (Fig: \ref{fig:betatwovalue})
* x-axis: difference preferences for circle $\beta^{\circ}_v - \beta^{\circ}_e$. x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\circ}_v - \beta^{\circ}_e = 5$ top panel, $\beta^{\circ}_v - \beta^{\circ}_e = 510$ lower panel); proceding on x-axis, value matters more to circle than value ($\beta^{\circ}_v$ is constant, while $\beta^{\circ}_e$ decreases to 0)
* y-axis: ethnic and value segregation for circle and square
* bottom left box, where all square relocate randomly ($\beta$ circle = 0):

```{r betatwovalue,  fig.pos="H",fig.out="96%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }

@@

iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
